$Z_3$ topological order in the quantum dimer-pentamer model

### 2016-05-07 qdpm_paper.tex
changed figure sizes

\usepackage{color}
\usepackage{bm}%bold math
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{bbold}
\usepackage{setspace}
\usepackage{epstopdf}
\usepackage{scalerel}
\epstopdfsetup{update} % only regenerate pdf files when eps file is newer
\linespread{1}
\usepackage[export]{adjustbox}

@@

\newcommand*{\svrtmon}{%
      height=3.5ex,% adjust to suit
    ]{Symbols/sing_vrt_monomer.pdf} }
\newcommand*{\svrtdmr}{%
      height=3.5ex,% adjust to suit
    ]{Symbols/sing_vrt_dimer.pdf} }
\newcommand*{\svrttrmr}{%
      height=3.5ex,% adjust to suit
    ]{Symbols/sing_vrt_trimer.pdf} }
\newcommand*{\svrtquat}{%
      height=3.5ex,% adjust to suit
    ]{Symbols/sing_vrt_quatramer.pdf} }
\newcommand*{\svrtpent}{%
      height=3.5ex,% adjust to suit
    ]{Symbols/sing_vrt_pentamer.pdf} }

@@

Over the last several decades, experimental and theoretical work has demonstrated that strongly interacting quantum many-body systems support exotic quantum phases of matter not described by the Landau symmetry breaking paradigm. One class of such quantum phases of matter are topologically ordered quantum liquids~\cite{Wen1990}, first realized experimentally via the fractional quantum Hall effect~\cite{FQHE????}. Despite the absence of conventional symmetry breaking and a local order parameter, topological quantum liquids possess a non-trivial quantum order that distinguishes them from trivial liquid phases~\cite{Nayak2008}. Although not detectable by local operators, topological order arises due to a non-local entanglement structure that leaves a signatures in the bipartite entanglement entropy~\cite{Levin2006a,Kitaev2006b}. Such topological phases may provide the basis for fault-tolerant quantum information processing~\cite{Freedman2001,Kitaev2003}.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{table}
  \begin{tabular}{| l | c | c | c | c |}
  	\hline
    type & $n_v$ & $Q_v^{\rm{QDM}}$ & $Q_v^{\rm{FPLM}}$  &  \\
	\hline
    monomer & $0$ & -1 & -2 & $\svrtmon$ \\
	\hline
    dimer & $1$ & 0 & -1 &  $\svrtdmr$ \\
	\hline
    trimer & $2$ & 1 & 0 &  $\svrttrmr $ \\
	\hline
    tetramer & $3$ & 2 & 1 &  $\svrtquat$ \\
	\hline
    pentamer & $4$ & 3 & 2 &  $\svrtpent$ \\
	\hline
  \end{tabular}
  \caption{Defects where $n_v$ dimers touch a vertex and their associated $U(1)$ charges on the A sub-lattice in both the QDM and QFPLM. Defects on the B sub-lattice have opposite charge.}
  \label{tab:defects}
\end{table}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

%%%%%%%%%%%%%%%%%%%%%%%
    \begin{figure}
        \centering
        \includegraphics[width=0.75\columnwidth]{dimer_gry_scale_qdpm.pdf}
        \caption{Gray scale of the dimer correlation function between the dimer in the upper
        left corner (colored red) and all other dimers on a $16\times16$ lattice. The 
         red dimers indicate correlations that are off the scale shown at the
        bottom of the figure. \textcolor{red}{Owen: make the origin dimer a different color that the off-scale dimers}.}
        \label{fig:dimer_gry_scale_qdpm}
    \end{figure}
%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}
    \centering
    \includegraphics[width=1.0\columnwidth]{spacial_dmr_cor.pdf}
    \caption{Correlation function between parallel dimers one the same (blue) and different (red) 
    sub-lattice on an $L=32$ lattice. The lines represent least-squares fits to exponential decay. }
    \label{fig:spatial_dmr_cor}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%
   \begin{figure}[]
        \centering
        \includegraphics[width=0.75\columnwidth]{qdpm_dmr_vis_HM_16x16.pdf}
        \caption{QDPM dimer structure factor $\gamma=0.5$.}
        \label{fig:spacial_dmr_z3vis_cor}
    \end{figure}
%%%%%%%%%%%%%%%%%%%%%%%

>>>>

\usepackage{color}
\usepackage{bm}%bold math
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{bbold}
\usepackage{setspace}
\usepackage{epstopdf}
%\usepackage{scalerel}
\epstopdfsetup{update} % only regenerate pdf files when eps file is newer
\linespread{1}
\usepackage[export]{adjustbox}

@@

@@

Over the last several decades, experimental and theoretical work has demonstrated that strongly interacting quantum many-body systems support exotic quantum phases phases of matter not described by the Landau symmetry breaking paradigm. One class of such quantum phases of matter are topologically ordered quantum liquids~\cite{Wen1990}, first realized experimentally via the fractional quantum Hall effect~\cite{FQHE????}. Despite the absence of conventional symmetry breaking and a local order parameter, topological quantum liquids possess a non-trivial quantum order that distinguishes them from trivial liquid phases~\cite{Nayak2008}. Although not detectable by local operators, topological order arises due to a non-local entanglement structure that leaves a signatures in the bipartite entanglement entropy~\cite{Levin2006a,Kitaev2006b}. Such topological phases may provide the basis for fault-tolerant quantum information processing~\cite{Freedman2001,Kitaev2003}.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{table}
  \begin{tabular}{| l | c | c | c |}
  	\hline
      	type & $n_v$ & $Q_v^{\rm{QDM}}$ & $Q_v^{\rm{FPLM}}$  \\
	\hline
	monomer & $0$ & -1 & -2 \\
	\hline
	dimer & $1$ & 0 & -1 \\
	\hline
	trimer & $2$ & 1 & 0 \\
	\hline
	tetramer & $3$ & 2 & 1 \\
	\hline
	pentamer & $4$ & 3 & 2 \\
	\hline
  \end{tabular}
  \caption{Defects where $n_v$ dimers touch a vertex and their associated $U(1)$ charges on the A sub-lattice in both the QDM and QFPLM. Defects on the B sub-lattice have opposite charge.}
  \label{tab:defects}
\end{table}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

%%%%%%%%%%%%%%%%%%%%%%%
    \begin{figure}
        \centering
        \includegraphics[width=0.5\columnwidth]{dimer_gry_scale_qdpm.pdf}
        \caption{Gray scale of the dimer correlation function between the dimer in the upper
        left corner (colored red) and all other dimers on a $16\times16$ lattice. The 
         red dimers indicate correlations that are off the scale shown at the
        bottom of the figure. \textcolor{red}{Owen: make the origin dimer a different color that the off-scale dimers}.}
        \label{fig:dimer_gry_scale_qdpm}
    \end{figure}
%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}
    \centering
    \includegraphics[width=1.0\columnwidth]{spacial_dmr_cor.pdf}
    \caption{Correlation function between parallel dimers one the same (blue) and different (red) 
    sub-lattice on an $L=32$ lattice. The lines represent least-squares fits to exponential decay. }
    \label{fig:spatial_dmr_cor}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%
   \begin{figure}[]
        \centering
        \includegraphics[width=1.0\columnwidth]{qdpm_dmr_vis_HM_16x16.pdf}
        \caption{QDPM dimer structure factor $\gamma=0.5$.}
        \label{fig:spacial_dmr_z3vis_cor}
    \end{figure}
%%%%%%%%%%%%%%%%%%%%%%%
